Weak interspecific interactions in a sagebrush steppe: Evidence from observational data, population models, and a removal experiment

### 2017-01-12 removals/manuscript/removal_ms.tex
More minor edits to figures

To quantify the short-term population-level consequences of removals, we used an IBM to project the cover of each species in each quadrat one year ahead using versions of the model with and without removal treatment effects. Our models tended to under-predict population growth (Fig. \ref{fig:CoverChange}) and population size (Fig. \ref{fig:IBM1step}) for all species, but the difference between predictions from the baseline and removal models varied among species. For \textit{A. tripartita}, both observed and predicted population growth rates were close to zero, and differences in model predictions were small. \textit{H. comata} experienced greater variation in growth rates, but the inclusion of removal treatment effects had little effect on population growth rates. For \textit{Poa secunda} and especially \textit{P. spicata}, the model with removal effects consistently predicted higher population growth than the baseline model (Fig. \ref{fig:CoverChange}), and reduced the underestimates of cover (Fig. \ref{fig:IBM1step}). The version of the model with maximum removal treatment effects (removal coefficients set to the 95\% confidence limit furthest from zero), were qualitatively similar, but further amplified the contrast between predictions of the baseline and removal models for and \textit{P. spicata} (Fig. \ref{fig:IBM1step-maxCI}). Across species, our baseline model tended to underpredict annual growth rates in control plots, but the correlation between observations and predictions was strong (Fig. \ref{fig:ObsPred1to1}A). In removal plots, we see greater underprediction of growth rates in certain years, especially for \textit{H. comata} and \textit{P. spicata}, but including removal treatment effects only slightly reduces this bias (Fig. \ref{fig:ObsPred1to1}B).

@@

>>>>

To quantify the short-term population-level consequences of removals, we used an IBM to project the cover of each species in each quadrat one year ahead using versions of the model with and without removal treatment effects. Our models tended to under-predict population growth (Fig. \ref{fig:CoverChange}) and population size (Fig. \ref{fig:IBM1step}) for all species, but the difference between predictions from the baseline and removal models varied among species. For \textit{A. tripartita}, both observed and predicted population growth rates were close to zero, and differences in model predictions were small. \textit{H. comata} experienced greater variation in growth rates, but the inclusion of removal treatment effects had little effect on population growth rates. For \textit{Poa secunda} and especially \textit{P. spicata}, the model with removal effects consistently predicted higher population growth than the baseline model  and reduced the underestimates of cover (Fig. \ref{fig:IBM1step}). Viewing all annual growth rates across species and years shows the same pattern of underprediction for some species, but also reveals a strong correlation between observations and predictions in control plots (Fig. \ref{fig:ObsPred1to1}A). In removal plots, underprediction of growth rates in certain years was larger, especially for \textit{H. comata} and \textit{P. spicata}; including removal treatment effects only slightly reduced this bias (Fig. \ref{fig:ObsPred1to1}B). For the version of the model with maximum removal treatment effects (removal coefficients set to the 95\% confidence limit furthest from zero), the patterns were qualitatively similar, with a somewhat greater contrast between predictions of the baseline and removal models for \textit{P. secunda} and \textit{P. spicata} (Figs. \ref{fig:IBM1step-maxCI},\ref{fig:ObsPred1to1-maxCI}).

@@

   \begin{figure}[tbp]
   \centering
   \includegraphics[width=1\textwidth]{cover_change_1to1_maxCI}
   \caption{Comparison of observed and predicted annual per capita growth rates across species in (A) control and (B) removal treatments assuming maximum effects of removals. The black line is a 1:1 line. Solid symbols correspond to predictions form the baseline IBM (no removal effects) and open symbols in (B) show predictions from an IBM that includes removal treatment effects. Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r} }
   \label{fig:ObsPred1to1-maxCI}
   \end{figure}
